%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
 \name{Mike Liao}
\address{1801 Briarwood Drive \linebreak Santa Clara CA 95051}
\contacts{(408) 318-2027 \linebreak mikeliao97@berkeley.edu
					\linebreak github.com/mikeliao97}


\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Berkeley, California}{University of California, Berkeley}{Fall 2011 - June 2019}
			\textbf{GPA: 3.7}			
			\begin{itemize}
				\item Bachelor's Degree in Computer Science, Expected
				\item Undergraduate Coursework: Data Structures(Java); The Structure and Interpretation of Computer Programs(Python); Discrete Math and Probability; Linear Algebra.
				\item Outside Coursework: The Odin Project: Web Development with Ruby on Rails; Stanford Database Course; Deanza Introduction to Big Data Analytics; Introduction to Java; 
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Projects}
		\begin{cvsubsection}{Independent Projects}{}{}
			\begin{itemize}
				\item \textbf{Take Me Somewhere} (http://devpost.com/software/take-me-somewhere). "Tinder-like" web application that recommends travel destinations based on user preferences. Ruby on Rails. 
				\item \textbf{Twitter Bot} (https://github.com/mikeliao97/twitterBot). Command-line tool to tweet posts, DM users, and keep track of friends' posts. Ruby. Twitter API.
				\item \textbf{Members Only} (https://github.com/mikeliao/members\_only) A private virtual online message board where users can signup to read/edit posts. Complete with a SQLite database and cookies/sessions functionality to remember users. Ruby on Rails. 
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Class Projects}{}{}
			\begin{itemize}
				\item \textbf{Text Editor} Functional text editor complete with many features: cursor clicking, backspace, newlines, arrow keys, font adjustment, word wrap, window resizing, open/save, scrollbar, undo/redo. Carefully implemented a data structure such that insertion, deletion, clicking, undo/redo runs in O(1) time. Java. JavaFX.
				\item \textbf{Bear Maps}  Crude ``Google-Maps'' application of the Berkeley Area. Users can zoom-in, zoom-out, and drag to view different parts of the map. Application also helps users find the shortest path between two destinations on the map using the A* search algorithm. Java. XML.
				\item \textbf{Restaurant Recommender} A map visualizer that predicts user's favorite restaurants in Berkeley based on user preferences. Implemented a k-means cluster algorithm that predicts areas in Berkeley where users can find their favorite restaurants. Python. Yelp API. 
				\item \textbf{Analysis of Breast Cancer}  Analyzed wether breast cancer cells were "malignant" or "benign" based on several factors such as "clump-thickness", "uniformity of cell size", and "marginal adhesion." Used WEKA and Java to apply a greedy ID3 algorithm that minimizes entropy and finds the best predictor of "malignant" based on these factors. Java. WEKA. UCI Machine Learning Dataset.
			\end{itemize}
		\end{cvsubsection}
		
	\end{cvsection}
	
	\begin{cvsection}{Experience and Awards}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Princeton Hacks Finalist (2015):} Worked independently on Take Me Somewhere, which helped place top 8 out of over 80 teams. Presented my application enthusiastically in front of judges and venture capitalists.
				\item \textbf{DECA States Entrepreneurship Finalist} (https://github.com/rdhanaraj/tsh) Placed 2nd out of 100 teams by helping pitch a friend's application that allows one to access web services like Facebook through text. Experienced with presenting and demoing applications in front of judges.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Previous Experience: Ruby, Java, Python, Ruby on Rails; SQL; Javascript; HTML
				\item Frameworks/Tools Git; Vim;
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
